Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-21 src/tex/ms.tex
update abstract

\begin{abstract}
    We present a simple and general method of recalibrating gravitational wave
    (GW) phenomenological waveform models jointly. By using {\jax} and
    {\ripple}, we can perform automatic differentiation to functions, which
    allows us to use gradient-based optimization methods to recalibrate waveform
    coefficients in IMRPhenomD model. This method reduces systematic bias
    previously introduced to the model and generally can improve waveform
    accuracy. With recalibrated coefficients, we found that the typical
    \textit{mismatch} has a $50\%$ decrease. Furthermore, we analyze the
    accuracy base on the waveform's intrinsic parameters. We found that waveform
    accuracy has significant dependence on black hole spin. Reduced spin
    approximation introduces degeneracy in spin, which prevented further
    improvement. We isolated regions in the parameter space that does not fit
    the waveform ansatz. These results allow us to understand more about how to
    develop newer phenomenological models. 
\end{abstract}

>>>>

\begin{abstract}
	We investigate the possibility of improving the accuracy of a
	phenomenological waveform model, IMRPhenomD, by jointly optimizing all the
	calibration coefficients at once, given a set of numerical relativity (NR)
	waveforms. When IMRPhenomD was first calibrated to NR waveforms, different
	parts of the waveform were calibrated separately. Using \ripple, a library
	of waveform models compatible with automatic differentiation, we can perform
	gradients-based optimization to all the waveform coefficients the same time,
	which should improve the quality of waveform by capturing correlations
	between previous separately fitted parts. We found that after recalibration,
	the median mismatch between the model and NR waveforms decrease by $50\%$.
	We further explore how different parts of the source parameter space respond
	to the optimization procedure. We find that the degree of improvement
	correlates with the spins of the source. This work shows a promising avenue
	to help understand and treat systematic error in waveform models.
\end{abstract}
